Methods

### 2023-10-11 Analysis/e2_test.qmd
create combined doc

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
testE2 <- readRDS(here("data/e2_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

>>>>

```{r setup2b, include=FALSE}
source(here::here("Functions", "packages.R"))
testE2 <- readRDS(here("data/e2_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

### 2023-10-11 Analysis/e3_test.qmd
create combined doc

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
testE3 <- readRDS(here("data/e3_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

>>>>

```{r setup3b, include=FALSE}
source(here::here("Functions", "packages.R"))
testE3 <- readRDS(here("data/e3_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

### 2023-10-11 Analysis/methods.qmd
create combined doc

```{r setup}
source(here::here("Functions", "packages.R"))
e1 <- readRDS(here("data/e1_08-04-23.rds")) 
e2 <- readRDS(here("data/e2_08-04-23.rds")) 
e3 <- readRDS(here("data/e3_08-04-23.rds"))

>>>>

```{r}
source(here::here("Functions", "packages.R"))
e1 <- readRDS(here("data/e1_08-04-23.rds")) 
e2 <- readRDS(here("data/e2_08-04-23.rds")) 
e3 <- readRDS(here("data/e3_08-04-23.rds"))
